full title

### 2020-11-21 paper/pldi21/javascript.tex
Till Sec. 4.3

We define the symbolic states with the extended concrete values and the abstract
counters for addresses as follows:
\[
  \begin{array}{r@{~}c@{~}l}
    \symbstset &=& \labset \times \memset \times \ctxtset \times \eaddrset
    \times \abscountset\\
    \ctxtset &=& \eaddrset \finmap ((\eaddrset \times \labset \times \locset)
    \uplus \symbset)\\
    \valset &=& \pvalset \uplus \oaddrset \uplus \fvalset \uplus \symbset\\
    \abscountset &=& \oaddrset \rightarrow \{ \abszero, \absone, \absmany \}\\
  \end{array}
\]
We define the converter $\asconverter: (\viewset \times \absdom) \rightarrow
(\absimapset \times \symbstset)$ from pairs of views and abstract states to the
corresponding pairs of abstract instantiation maps and sealed symbolic states.
The algorithm is to traverse the averall structure, to remain a single value,
but changes to each abstract value represents multiple values to a new symbol
and adds the mapping from the new symbol to the original abstract value.  In a
reverse way, the opposite converter $\saconverter: (\absimapset \times
\symbstset)  \rightarrow (\viewset \times \absdom)$ recovers the abstract values
based on the given abstract instantiation map.  The symbolic transition relation
$\symbtrans$ is an extension of the original concrete transition relation
$\trans$.  When the exact values of symbolic values are required, symbolic
states have the symbolic transition relation with the exception state $\excst$.
For example, we add the following rule for $\kwret$ statements:
\begin{mathpar}
  \inferrule
  {
    \prog(\lab) = \kwret \; \expr\\
    \exprrule{\st}{\expr}{\val}\\
    \ctxt(\addr) \in \symbset
  }
  {
    \st = (\lab, \mem, \ctxt, \addr)
    \trans \excst
  }
\end{mathpar}
We extend each rule of concrete semantics to support such behaviors of symbolic
values.

>>>>

We define the sealed symbolic states by not only extending the concrete values
$\valset$ with symbolic values $\symbset$ but also adding the abstract counters
$\abscountset$ as follows:
\[
  \begin{array}{r@{~}c@{~}l}
    \symbstset &=& \labset \times \memset \times \ctxtset \times \eaddrset
    \times \abscountset\\
    \ctxtset &=& \eaddrset \finmap ((\eaddrset \times \labset \times \locset)
    \uplus \symbset)\\
    \valset &=& \pvalset \uplus \oaddrset \uplus \fvalset \uplus \symbset\\
    \abscountset &=& \oaddrset \rightarrow \{ \abszero, \absone, \absmany \}\\
  \end{array}
\]
Because JavaScript provides open objects, the properties of objects can be dynamically added or deleted.
Moreover, since object properties are string values that can be constructed at run time,
it is difficult for static analysis to know whether strong udpates are possible or not.
To check the possibility of strong updates during sealed symbolic execution,
we augment its states with the abstract counters $\abscountset$.

For each abstract value in a given abstract state,
if the abstract value denotes a single concrete value,
the converter $\asconverter: (\viewset \times
\absdom) \rightarrow (\absimapset \times \symbstset)$
keeps it as it is; otherwise, $\asconverter$ replaces the abstract
value with its unique identifier and maintains the mapping from the
unique identifier to the abstract value to construct an abstract instantiation map.
The opposite converter $\saconverter: (\absimapset \times
  \symbstset)  \rightarrow (\viewset \times \absdom)$
recovers abstract values from their unique identifiers using the abstract instantiation map.
We define the sealed symbolic transition relation $\symbtrans$
only if the next step does not require actual values of any symbolic values.
Otherwise, a given sealed symbolic state does not have any sealed symbolic
transitions to apply.  For example, we add the following rule for the $\kwret$ statement:
\begin{mathpar}
  \inferrule
  {
    \prog(\lab) = \kwret \; \expr\\
    \exprrule{\symbst}{\expr}{\val}\\
    \ctxt(\addr) \in \symbset
  }
  {
    \symbst = (\lab, \mem, \ctxt, \addr, \abscount)\
    \symbtrans \excst
  }
\end{mathpar}
We extend each rule of the concrete semantics to support such behaviors of symbolic
values.
